% A cleaned version of the Dart grammar that was extracted from the language specification (Version 1.11)
 
\begin{grammar}
{\bf variableDeclaration:}
    declaredIdentifier (',' identifier)*
    .

{\bf declaredIdentifier:}
    metadata finalConstVarOrType identifier
    .

{\bf finalConstVarOrType:}
    'final' type?;
    'const' type?;
    varOrType
    .

{\bf varOrType:}'var';
    type
    .

{\bf initializedVariableDeclaration:}
    declaredIdentifier ('=' expression)? (',' initializedIdentifier)*
    .

{\bf initializedIdentifier:}
    identifier ('=' expression)?
    .

{\bf initializedIdentifierList:}
    initializedIdentifier (',' initializedIdentifier)*
    .
\end{grammar}
\begin{grammar}
{\bf functionSignature:}
    metadata returnType? identifier formalParameterList
    .
    
{\bf returnType:}
    'void';
    type
    .

{\bf functionBody:}
    'async'?  '=>' expression ';';
    ('async' ; 'async'* ; 'sync'*)? block
    .

{\bf block:}
    '\{' statements '\}'
    .
\end{grammar}
\begin{grammar}
{\bf formalParameterList:}
    '(' ')';
    '(' normalFormalParameters ( ','  optionalFormalParameters)? ')';
    '(' optionalFormalParameters ')'
    .
\end{grammar}
\begin{grammar}
{\bf normalFormalParameters:}
    normalFormalParameter (',' normalFormalParameter)*
    .

{\bf optionalFormalParameters:}
    optionalPositionalFormalParameters;
    namedFormalParameters
    .

{\bf optionalPositionalFormalParameters:}
    '[' defaultFormalParameter (',' defaultFormalParameter)* ']'
    .

{\bf namedFormalParameters:}
    '\{' defaultNamedParameter (',' defaultNamedParameter)* '\}'
    .
\end{grammar}
\begin{grammar}
{\bf normalFormalParameter:}functionSignature;
    fieldFormalParameter;
    simpleFormalParameter
    .

{\bf simpleFormalParameter:}
    declaredIdentifier;
    metadata identifier
    .

{\bf fieldFormalParameter:}
    metadata finalConstVarOrType? 'this' '.' identifier formalParameterList?
    .
\end{grammar}
\begin{grammar}
{\bf defaultFormalParameter:}
    normalFormalParameter ('=' expression)?
    .   
        
{\bf defaultNamedParameter:}
    normalFormalParameter ( ':' expression)?
    .   
\end{grammar}
\begin{grammar}
{\bf classDefinition:}
    metadata 'abstract'?  'class' identifier typeParameters? (superclass mixins?)? interfaces?
    '\{' (metadata classMemberDefinition)* '\}';
    metadata 'abstract'?  'class' mixinApplicationClass
    .
    
{\bf mixins:}
    \WITH{} typeList
    .

{\bf classMemberDefinition:}
    declaration ';';
    methodSignature functionBody
    .

{\bf methodSignature:}
    constructorSignature initializers?;
    factoryConstructorSignature;
    \STATIC{}? functionSignature;
    \STATIC{}? getterSignature;
    \STATIC{}? setterSignature;
    operatorSignature
    .

{\bf declaration:}
    constantConstructorSignature (redirection ; initializers)?;
    constructorSignature (redirection ; initializers)?;
    'external' constantConstructorSignature;
    'external' constructorSignature;
    (('external' \STATIC{}?))? getterSignature;
    (('external' \STATIC{}?))? setterSignature;
    'external'? operatorSignature;
     (('external' \STATIC{}?))? functionSignature;
    \STATIC{} ('final' ; 'const') type? staticFinalDeclarationList;
    'final' type? initializedIdentifierList;
    \STATIC{}? ('var' ; type) initializedIdentifierList
    .

{\bf staticFinalDeclarationList:}
    staticFinalDeclaration (',' staticFinalDeclaration)*
    .

{\bf staticFinalDeclaration:}
    identifier '=' expression
    .
\end{grammar}
\begin{grammar}
{\bf operatorSignature:}
    returnType? \OPERATOR{} operator formalParameterList
    .
       
{\bf operator:}
    '~';
    binaryOperator;
    '[' ']' ;
    '[' ']' '='
    .

{\bf binaryOperator:}multiplicativeOperator;
    additiveOperator;
    shiftOperator;
    relationalOperator;
    '==';
    bitwiseOperator
    .
\end{grammar}
\begin{grammar}
{\bf getterSignature:}
    returnType? \GET{} identifier 
    .
\end{grammar}
\begin{grammar}
{\bf setterSignature:}
    returnType? \SET{} identifier formalParameterList
    .
\end{grammar}
\begin{grammar}
{\bf constructorSignature:}
    identifier ('.' identifier)? formalParameterList
    .
\end{grammar}
\begin{grammar}
{\bf redirection:}
    ':' 'this' ('.' identifier)? arguments
    .
\end{grammar}
\begin{grammar}
{\bf initializers:}
    ':' superCallOrFieldInitializer (',' superCallOrFieldInitializer)*
    .

{\bf superCallOrFieldInitializer:}
    'super' arguments;
    'super' '.' identifier arguments;
    fieldInitializer
    .
    
{\bf fieldInitializer:}
    ('this' '.')? identifier '=' conditionalExpression cascadeSection*
    .
\end{grammar}
\begin{grammar}
{\bf factoryConstructorSignature:}
    \FACTORY{} identifier  ('.' identifier)?  formalParameterList
    .
\end{grammar}
\begin{grammar}
{\bf constantConstructorSignature:}
    'const' qualified formalParameterList
    .
\end{grammar}
\begin{grammar}
{\bf superclass:}
    \EXTENDS{} type
    .
\end{grammar}
\begin{grammar}
{\bf interfaces:}
    \IMPLEMENTS{} typeList
    .
\end{grammar}
\begin{grammar}
{\bf  mixinApplicationClass:}
    identifier typeParameters? '='  mixinApplication ';'
    .

{\bf mixinApplication:}
    type mixins interfaces? 
    .
\end{grammar}
\begin{grammar}
{\bf enumType:}
    metadata \ENUM{} id '\{' id (',' id)* ','? '\}'
    .
\end{grammar}
\begin{grammar}
{\bf typeParameter:}
    metadata identifier (\EXTENDS{} type)?
    .
{\bf typeParameters:}
    '<' typeParameter (',' typeParameter)* '>'
    .
\end{grammar}
\begin{grammar}
{\bf metadata:}
    ('@' qualified ('.' identifier)? (arguments)?)*
    .
\end{grammar}
\begin{grammar}
{\bf expression:}
    assignableExpression assignmentOperator expression;
    conditionalExpression cascadeSection*;
    throwExpression     
    .

{\bf expressionWithoutCascade:}
    assignableExpression assignmentOperator expressionWithoutCascade;
    conditionalExpression;
    throwExpressionWithoutCascade    
    .

{\bf expressionList:}
    expression (',' expression)*
    .
\end{grammar}
\begin{grammar}
{\bf primary:}
    thisExpression;
    'super' unconditionalAssignableSelector;
    functionExpression;
    literal;
    identifier;
    newExpression;
    \NEW{} type '\#' ('.' identifier)?;
    constObjectExpression;
    '(' expression ')'
    .
\end{grammar}
\begin{grammar}
{\bf literal:}
    nullLiteral;
    booleanLiteral;
    numericLiteral;
    stringLiteral;
    symbolLiteral;
    mapLiteral;
    listLiteral
    .
\end{grammar}
\begin{grammar}
{\bf nullLiteral:}
    \NULL{}
    .
\end{grammar}
\begin{grammar}
{\bf numericLiteral:}
    NUMBER;
    HEX_NUMBER
    .
    
{\bf NUMBER:}
    DIGIT+ ('.' DIGIT+)? EXPONENT?;
    '.' DIGIT+ EXPONENT?
    .

{\bf EXPONENT:}
    ('e' ; 'E') ('+' ; '-')? DIGIT+
    .

{\bf HEX_NUMBER:}
    '0x' HEX_DIGIT+;
    '0X' HEX_DIGIT+
    .

 {\bf HEX_DIGIT:}
    'a'..'f';
    'A'..'F';
    DIGIT
    .
\end{grammar}
\begin{grammar}
{\bf booleanLiteral:}
    \TRUE{};
    \FALSE{}
    .
\end{grammar}
\begin{grammar}
{\bf stringLiteral:}
    (multilineString ; singleLineString)+
    .
\end{grammar}
\begin{grammar}
{\bf singleLineString:}
    '"' stringContentDQ* '"';
    '\'' stringContentSQ* '\'';
    'r' '\'' (~( '\' ; NEWLINE ))* '\'';
    'r' '"' (~( '"' ; NEWLINE ))* '"'
    .
\end{grammar}
\begin{grammar}
{\bf multilineString:}
    '"""' stringContentTDQ*   '"""';
    '\'\'\'' stringContentTSQ* '\'\'\'';
    'r' '"""'  (~ '"""')*   '"""';
    'r' '\'\'\'' (~ '\'\'\'')* '\'\'\''
    .

{\bf ESCAPE_SEQUENCE:}
    '\\n';
    '\\r';
    '\\f';
    '\\b';
    '\\t';
    '\\v';
    '\\x' HEX_DIGIT HEX_DIGIT;
    '\\u' HEX_DIGIT HEX_DIGIT HEX_DIGIT HEX_DIGIT;
    '\\u\{' HEX_DIGIT_SEQUENCE '\}'
    .

{\bf HEX_DIGIT_SEQUENCE:}
    HEX_DIGIT HEX_DIGIT? HEX_DIGIT? HEX_DIGIT? HEX_DIGIT? HEX_DIGIT? 
    .
\end{grammar}
\begin{grammar}
{\bf stringContentDQ:}
    ~( '\\' ; '"' ; '\$' ; NEWLINE );
    '\\'  ~( NEWLINE );
    stringInterpolation
    .

{\bf stringContentSQ:}
    ~( '\\' ; '\'' ; '\$' ; NEWLINE );
    '\\'  ~( NEWLINE );
    stringInterpolation
    .

{\bf stringContentTDQ:}
    ~( '\\' ;  '"""' ; '\$');
    stringInterpolation
    .    

{\bf stringContentTSQ:}
    ~( '\\' ; '\'\'\'' ; '\$');
    stringInterpolation
    .

{\bf NEWLINE:}
    '\\n';
    '\\r'
    .
\end{grammar}
\begin{grammar}
{\bf stringInterpolation:}
    '\$' IDENTIFIER_NO_DOLLAR;
    '\$' '\{' expression '\}'
    .
\end{grammar}
\begin{grammar}
{\bf symbolLiteral:}
    '\#'  (operator ; (identifier ('.' identifier)*))
    .
\end{grammar}
\begin{grammar}
{\bf listLiteral:}
    'const'? typeArguments? '[' (expressionList ','?)? ']'
    .
\end{grammar}
\begin{grammar}
{\bf mapLiteral:}
    'const'?  typeArguments? '\{' (mapLiteralEntry (',' mapLiteralEntry)* ','?)? '\}'
    .

{\bf mapLiteralEntry:}
    expression ':' expression 
    .
\end{grammar}
\begin{grammar}
{\bf throwExpression:}
    \THROW{} expression 
    .
    
{\bf throwExpressionWithoutCascade:}
    \THROW{} expressionWithoutCascade 
    .
\end{grammar}
\begin{grammar}
{\bf functionExpression:}
    formalParameterList functionBody
    .
\end{grammar}
\begin{grammar}
{\bf thisExpression:}
    'this'
    .
\end{grammar}
\begin{grammar}
{\bf newExpression:}
    \NEW{} type ('.' identifier)? arguments
    .
\end{grammar}
\begin{grammar}
{\bf constObjectExpression:}
    'const' type ('.' identifier)? arguments
    .
\end{grammar}
\begin{grammar}
{\bf arguments:}
    '(' argumentList? ')'
    .

{\bf argumentList:}
    namedArgument (',' namedArgument)*;
    expressionList (',' namedArgument)*
    .

{\bf namedArgument:}
    label expression
    .
\end{grammar}
\begin{grammar}
{\bf cascadeSection:}
    '..' (cascadeSelector arguments*) (assignableSelector arguments*)* (assignmentOperator expressionWithoutCascade)?
    .
     
{\bf cascadeSelector:}
    '['  expression ']';
    identifier
    .
\end{grammar}
\begin{grammar}
{\bf assignmentOperator:}
    '=' ;
    compoundAssignmentOperator
    .
\end{grammar}
\begin{grammar}
{\bf compoundAssignmentOperator:}
    '*=';
    '/=';
    '~/=';
    '\%=';
    '+=';
    '-=';
    '<<=';
    '>>=';
    '&=';
    '^=';
    ';=';
    '??='
    .
\end{grammar}
\begin{grammar}
{\bf conditionalExpression:}
    ifNullExpression ('?' expressionWithoutCascade ':' expressionWithoutCascade)?
    .
\end{grammar}
\begin{grammar}
{\bf ifNullExpression:}
    logicalOrExpression ('??' logicalOrExpression)*
    .
\end{grammar}
\begin{grammar}
{\bf logicalOrExpression:}
    logicalAndExpression ('$||$' logicalAndExpression)*
    .

{\bf logicalAndExpression:}
    equalityExpression ('\&\&' equalityExpression)*
    .
 \end{grammar}
\begin{grammar}
{\bf equalityExpression:}
    relationalExpression (equalityOperator relationalExpression)?;
    'super' equalityOperator relationalExpression
    .

{\bf equalityOperator:}
    '==';
    '!='
    .
\end{grammar}
\begin{grammar}
{\bf relationalExpression:}
    bitwiseOrExpression (typeTest ; typeCast ; relationalOperator bitwiseOrExpression)?;
    'super' relationalOperator bitwiseOrExpression
    .

{\bf relationalOperator:}
    '>=';
    '>';
    '<=';
    '<'
    .
\end{grammar}
\begin{grammar}
{\bf bitwiseOrExpression:}
    bitwiseXorExpression (';' bitwiseXorExpression)*;
    'super' (';' bitwiseXorExpression)+
    .

{\bf bitwiseXorExpression:}
    bitwiseAndExpression ('\^{}' bitwiseAndExpression)*;
    'super' ('\^{}' bitwiseAndExpression)+
    .

{\bf bitwiseAndExpression:}
    shiftExpression ('\&' shiftExpression)*;
    'super' ('\&' shiftExpression)+
    .

{\bf bitwiseOperator:}
    '&';
    '^';
    ';'
    .
\end{grammar}
\begin{grammar}
{\bf shiftExpression:}
    additiveExpression (shiftOperator additiveExpression)*;
    'super' (shiftOperator additiveExpression)+
    .

{\bf shiftOperator:}
    '<<';
    '>>' 
    .
\end{grammar}
\begin{grammar}
{\bf additiveExpression:}
    multiplicativeExpression (additiveOperator multiplicativeExpression)*;
    'super' (additiveOperator multiplicativeExpression)+
    .

{\bf additiveOperator:}
    '+';
    '-'
    .
\end{grammar}
\begin{grammar}
{\bf multiplicativeExpression:}
    unaryExpression (multiplicativeOperator unaryExpression)*;
    'super' (multiplicativeOperator unaryExpression)+
    .

{\bf multiplicativeOperator:}
    '*';
    '/';
    '\%';
    '~/'
    .    
\end{grammar}
\begin{grammar}
{\bf unaryExpression:}
    prefixOperator unaryExpression;
    awaitExpression;
    postfixExpression;
    (minusOperator ; tildeOperator) 'super';
    incrementOperator assignableExpression
    .
 
{\bf prefixOperator:}
    minusOperator;
    negationOperator;
    tildeOperator
    .

{\bf minusOperator:}
    '-'
    .

{\bf negationOperator:}
    '!'
    .
      
{\bf tildeOperator:}
    '~'
    .
\end{grammar}
\begin{grammar}
{\bf awaitExpression:}
    \AWAIT{} unaryExpression
    .
\end{grammar}
\begin{grammar}
{\bf postfixExpression:}
    assignableExpression postfixOperator;
    primary (selector* ; ( '\#' ( (identifier '='?) ; operator)))
    .

{\bf postfixOperator:}
    incrementOperator
    .

{\bf selector:}
    assignableSelector;
    arguments
    .

{\bf incrementOperator:}
    '++';
    '-{}-'
    .        
\end{grammar}
\begin{grammar}
{\bf assignableExpression:}
    primary (arguments* assignableSelector)+;
    'super' unconditionalAssignableSelector;
    identifier
    .
    
{\bf unconditionalAssignableSelector:}
    '[' expression ']';
    '.' identifier
    .

{\bf assignableSelector:}
    unconditionalAssignableSelector;
    '?.' identifier
    .
\end{grammar}
\begin{grammar}
{\bf identifier:}
    IDENTIFIER
    .

{\bf IDENTIFIER_NO_DOLLAR:}
    IDENTIFIER_START_NO_DOLLAR IDENTIFIER_PART_NO_DOLLAR*
    .

{\bf IDENTIFIER:}
    IDENTIFIER_START IDENTIFIER_PART*
    .

{\bf BUILT_IN_IDENTIFIER:}
    'abstract';
    \AS{};
    \DEFERRED{};
    \DYNAMIC{};
    \EXPORT{};
    'external';
    \FACTORY{};
    \GET{};
    \IMPLEMENTS{};
    \IMPORT{};
    \LIBRARY{};
    \OPERATOR{};
    \PART{};
    \SET{};
    \STATIC{};
    \TYPEDEF{}
    .

{\bf IDENTIFIER_START:}
    IDENTIFIER_START_NO_DOLLAR;
    '\$'
    .

{\bf IDENTIFIER_START_NO_DOLLAR:}
    LETTER;
    '_'
    .

{\bf  IDENTIFIER_PART_NO_DOLLAR:}
    IDENTIFIER_START_NO_DOLLAR;
    DIGIT
    .

{\bf IDENTIFIER_PART:}
    IDENTIFIER_START;
    DIGIT
    .

{\bf qualified:}
    identifier ('.' identifier)?  
    . 
\end{grammar}
\begin{grammar}
{\bf typeTest:}
    isOperator type
    .

{\bf isOperator:}
    \IS{} '!'?
    .
\end{grammar}
\begin{grammar}
{\bf typeCast:}
    asOperator type
    .

{\bf asOperator:}
    \AS{}
    .
\end{grammar}
\begin{grammar}
{\bf statements:}
    statement*
    .

{\bf statement:}
    label* nonLabelledStatement
    .

{\bf nonLabelledStatement:}
    block; 
    localVariableDeclaration;
    forStatement;
    whileStatement;
    doStatement;
    switchStatement;
    ifStatement;
    rethrowStatement;
    tryStatement;
    breakStatement;
    continueStatement;
    returnStatement;
    yieldStatement;
    yieldEachStatement;
    expressionStatement;
    assertStatement;
    localFunctionDeclaration
    .
\end{grammar}
\begin{grammar}
{\bf expressionStatement:}
    expression? ';'
    .
\end{grammar}
\begin{grammar}
{\bf localVariableDeclaration:}
    initializedVariableDeclaration ';'
    .
\end{grammar}
\begin{grammar}
{\bf localFunctionDeclaration:}
    functionSignature functionBody
    .
\end{grammar}
\begin{grammar}
{\bf ifStatement:}
    \IF{} '(' expression ')' statement ( \ELSE{} statement)?
    .
\end{grammar}
\begin{grammar}
{\bf forStatement:}
    \AWAIT? \FOR{} '(' forLoopParts ')' statement
    .

{\bf forLoopParts:}
    forInitializerStatement expression? ';' expressionList?;
    declaredIdentifier \IN{} expression;
    identifier \IN{} expression
    .

{\bf forInitializerStatement:}
    localVariableDeclaration;
    expression? ';'
    .
\end{grammar}
\begin{grammar}
{\bf whileStatement:}
    \WHILE{} '(' expression ')' statement
    .
\end{grammar}
\begin{grammar}
{\bf doStatement:}
    \DO{} statement \WHILE{} '(' expression ')' ';'
    .
\end{grammar}
\begin{grammar}
{\bf switchStatement:}
    \SWITCH{} '(' expression ')' '\{' switchCase* defaultCase? '\}'
    .

{\bf switchCase:}
    label* \CASE{} expression ':' statements
    .

{\bf defaultCase:}
    label*  \DEFAULT{} ':' statements
    .
\end{grammar}
\begin{grammar}
{\bf rethrowStatement:}
    \RETHROW{}  ';'
    .
\end{grammar}
\begin{grammar}
{\bf tryStatement:}
    \TRY{} block (onPart+ finallyPart? ; finallyPart)
    .

{\bf onPart:}catchPart block;
    \ON{} type catchPart? block
    .

{\bf catchPart:}
    \CATCH{} '(' identifier (',' identifier)? ')' 
    .

{\bf finallyPart:}
    \FINALLY{} block
    .
\end{grammar}
\begin{grammar}
{\bf returnStatement:}
    \RETURN{} expression? ';'
    .
\end{grammar}
\begin{grammar}
{\bf label:}
    identifier ':'
    .
\end{grammar}
\begin{grammar}
{\bf breakStatement:}
    \BREAK{} identifier? ';'
    .
\end{grammar}
\begin{grammar}
{\bf continueStatement:}
    \CONTINUE{} identifier? ';'
    .
\end{grammar}
\begin{grammar}
{\bf yieldStatement:}
    \YIELD{} expression ';'
    .
\end{grammar}
\begin{grammar}
{\bf yieldEachStatement:}
    \YIELD* expression ';'
    .
\end{grammar}
\begin{grammar}
{\bf assertStatement:}
    assert '(' conditionalExpression ')' ';'
    .
\end{grammar}
\begin{grammar}
% TODO: topLevelDefinition leaves no way to parse "var int x = 1, y = 2", but
% it is a valid Dart program. Why are staticFinalDeclarationList and
% variableDeclaration distinguished? Can we merge this, e.g. by using
% initializedVariableDeclaration?

{\bf topLevelDefinition:}classDefinition;
    enumType;
    typeAlias;
    'external'? functionSignature ';';
    'external'? getterSignature ';';
    'external'? setterSignature ';';      
    functionSignature functionBody;
    returnType? \GET{} identifier functionBody;
    returnType? \SET{} identifier formalParameterList functionBody;
    ('final' ; 'const') type? staticFinalDeclarationList ';';
    variableDeclaration ';'
    .

{\bf libraryDefinition:}
    scriptTag? libraryName? importOrExport* partDirective* topLevelDefinition*
    .
    
{\bf scriptTag:}
    '\#!' (~NEWLINE)* NEWLINE
    .

{\bf libraryName:}
    metadata \LIBRARY{} identifier ('.' identifier)* ';'
    .

{\bf importOrExport:}
    libraryImport ;
    libraryExport
    .
\end{grammar}
\begin{grammar}
{\bf libraryImport:}
    metadata importSpecification
    .
 
{\bf importSpecification:}
    \IMPORT{}  uri (\AS{} identifier)?  combinator* ';';
    \IMPORT{}  uri \DEFERRED{} \AS{} identifier  combinator* ';'
    .
     
{\bf combinator:}
    \SHOW{} identifierList;
    \HIDE{} identifierList
    .
    
{\bf identifierList:}
    identifier (',' identifier)*
    .
\end{grammar}
\begin{grammar}
{\bf libraryExport:}
    metadata \EXPORT{}  uri  combinator* ';'
    .
\end{grammar}
\begin{grammar}
{\bf partDirective:}
    metadata \PART{}   uri ';' 
    .

{\bf partHeader:}
    metadata \PART{} \OF{} identifier ('.' identifier)* ';'
    .

{\bf partDeclaration:}
    partHeader topLevelDefinition* EOF
    .
\end{grammar}
\begin{grammar}
{\bf uri:}
    stringLiteral
    .
\end{grammar}
\begin{grammar}
{\bf type:}
    typeName typeArguments?
    .

{\bf typeName:}
    qualified 
    .

{\bf typeArguments:}
    '<' typeList '>'
    .

{\bf typeList:}
    type (',' type)*
    .
 \end{grammar}
\begin{grammar}

{\bf typeAlias:}
    metadata \TYPEDEF{} typeAliasBody
    .
  
{\bf typeAliasBody:}
    functionTypeAlias
    .

{\bf functionTypeAlias:}
    functionPrefix typeParameters? formalParameterList ';'
    .
    
{\bf functionPrefix:}
    returnType? identifier
    .    
\end{grammar}
\begin{grammar}
{\bf LETTER:}
    'a' .. 'z';
    'A' ..'Z'
    .

{\bf DIGIT:}
    '0' .. '9'
    .

{\bf WHITESPACE:}
    ('$\backslash$t' ; ' ' ; NEWLINE)+
    .
\end{grammar}
\begin{grammar}
{\bf SINGLE_LINE_COMMENT:}
    '//' ~(NEWLINE)* (NEWLINE)?
    .

{\bf MULTI_LINE_COMMENT:}
    '/*' (MULTI_LINE_COMMENT ; ~ '*/')* '*/'
    .
\end{grammar}